---
title: 'PA: Course Project: Shiny Application and Reproducible Pitch'
author: "Tomoki Ito"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Individual household electric power consumption Data Set

Data Set Information:

This archive contains 2075259 measurements gathered in a house located in Sceaux (7km of Paris, France) between December 2006 and November 2010 (47 months).

For more details on [UCI Machine Learning Repository](https://archive.ics.uci.edu/ml/datasets/individual+household+electric+power+consumption)


## loading library and reading Dataset 

```{r echo = TRUE,message=FALSE,warning=FALSE}
library(tidyverse)
library(lubridate)
library(tibbletime)
library(plotly)
library(rsconnect)
```

```{r echo = TRUE,cache=TRUE}
# Read data
mydata <- read.table("household_power_consumption.txt",
                     header=T,na.strings="?",sep=";") %>%
                     as_data_frame
# Select dates from "2007-01-01" to "2007-12-31"
mydata2 <- mydata %>% 
        mutate(Date = dmy_hms(paste(mydata$Date,mydata$Time))) %>% 
        as_tbl_time(index = Date) %>% 
        select(-Time) %>% 
        filter_time(time_formula = "2007-01-01" ~ "2007-12-31")

```

## Shiny Application
the Link for the Application.  
https://tomokiito-course.shinyapps.io/pa_w4/

the link for github repo.  
https://github.com/tomokiito/Shiny-Application-and-Reproducible-Pitch

## Thank you!
